---
title: "Weather Forecast Report"
author: "Syed Abu Hasnat"
date: "2026-02-04"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### Installing the packages
install.packages("tinytex")
tinytex::install_tinytex()

# Weather Forecast Report

## Introduction

The weather forecast for the upcoming week is as follows:

- Monday: *Sunny* with temperatures around **25째C**
- Tuesday: *Cloudy* with temperatures around **22째C**
- Wednesday: *Rainy* with temperatures around **20째C**

### Data Analysis

### Creating Temperature Data

```{r temperature-data}
days <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
temperatures <- c(25, 22, 20, 23, 24)
days
temperatures
```

### Plot Weekly Temperature Forecast

```{r temperature-plot}
barplot(
  temperatures,
  names.arg = days,
  col = "skyblue",
  main = "Weekly Temperature Forecast",
  xlab = "Days",
  ylab = "Temperature (째C)"
)
```


## Conclusion

This Weather Forecast Report demonstrates how R Markdown can be used to format text, analyze data, visualize results, and generate a professional PDF report.


